---
execute:
  echo: false
  warning: false
  message: false
  cache: false
  freeze: false
---

```{r}
library(yaml)
library(htmltools)

students <- yaml::read_yaml("data/students.yml")

esc <- function(x) htmltools::htmlEscape(as.character(x))

get_value <- function(x, name, default = "") {
  if (!is.null(x[[name]])) x[[name]] else default
}

slugify <- function(x) {
  x <- tolower(x)
  x <- gsub("[^a-z0-9]+", "-", x)
  x <- gsub("^-|-$", "", x)
  x
}

make_tags <- function(topics) {
  if (length(topics) == 0) return("")
  paste0(
    vapply(
      topics,
      function(topic) {
        paste0('<a class="tag" href="#', slugify(topic), '">', esc(topic), '</a>')
      },
      character(1)
    ),
    collapse = "\n"
  )
}

make_links <- function(links) {
  if (length(links) == 0) return("")
  valid_links <- links[vapply(links, function(x) !is.null(x$url) && x$url != "#", logical(1))]
  if (length(valid_links) == 0) return("")

  paste(
    vapply(
      valid_links,
      function(x) paste0('<a href="', esc(x$url), '">', esc(x$text), '</a>'),
      character(1)
    ),
    collapse = " · "
  )
}

make_articles <- function(articles) {
  if (length(articles) == 0) return("")

  items <- vapply(
    articles,
    function(a) {
      title <- esc(get_value(a, "title"))
      url <- get_value(a, "url", "#")
      if (!is.null(url) && url != "#") {
        paste0('<li><a href="', esc(url), '">', title, '</a></li>')
      } else {
        paste0('<li>', title, '</li>')
      }
    },
    character(1)
  )

  paste0(
    '<div class="student-articles"><strong>Articles from thesis</strong><ul>',
    paste(items, collapse = "\n"),
    '</ul></div>'
  )
}

make_coadvisors <- function(co_advisors) {
  if (length(co_advisors) == 0) return("")
  paste0(
    '<div class="student-meta"><strong>Co-advising:</strong> ',
    esc(paste(co_advisors, collapse = ", ")),
    '</div>'
  )
}

make_card <- function(s) {
  links_html <- make_links(get_value(s, "links", list()))

  if (links_html != "") {
    links_html <- paste0('<div class="student-links">', links_html, '</div>')
  }

  paste0(
    '<div class="student-card" id="', esc(get_value(s, "id")), '">\n',
    '<h3>', esc(get_value(s, "name")), '</h3>\n',
    '<div class="student-meta"><strong>', esc(get_value(s, "degree_type")), ' alumnus</strong> · Defense: ', esc(get_value(s, "year")), '</div>\n',
    '<div class="student-meta">', esc(get_value(s, "degree")), '</div>\n',
    make_coadvisors(get_value(s, "co_advisors", list())), '\n',
    '<p class="student-thesis"><strong>Thesis:</strong> ', esc(get_value(s, "thesis")), '</p>\n',
    '<p><strong>Current position:</strong> ', esc(get_value(s, "current_position")), '</p>\n',
    make_tags(get_value(s, "topics", list())), '\n',
    make_articles(get_value(s, "articles", list())), '\n',
    links_html, '\n',
    '</div>\n'
  )
}

students <- students[order(vapply(students, function(s) -as.numeric(get_value(s, "year", 0)), numeric(1)))]

n_total <- length(students)
n_master <- sum(vapply(students, function(s) get_value(s, "degree_type") == "Master", logical(1)))
n_phd <- sum(vapply(students, function(s) get_value(s, "degree_type") == "PhD", logical(1)))

all_topics <- sort(unique(unlist(lapply(students, function(s) get_value(s, "topics", list())))))
```

# Students & Alumni

I have advised graduate students working on applied econometrics, spatial econometrics, discrete choice models, causal inference, environmental economics, health economics, education, and human capital.

::: {.student-summary}
::: {.student-stat}
**`r n_total`**  
Graduate alumni
:::

::: {.student-stat}
**`r n_master`**  
Master alumni
:::

::: {.student-stat}
**`r n_phd`**  
PhD alumni
:::
:::

## Research areas {#research-areas}

```{r}
#| results: asis

for (topic in all_topics) {
  cat('<a class="tag" href="#', slugify(topic), '">', esc(topic), '</a>\n', sep = "")
}
```

---

## Doctoral alumni {#doctoral-alumni}

```{r}
#| results: asis

selected <- students[vapply(students, function(s) get_value(s, "degree_type") == "PhD", logical(1))]

if (length(selected) == 0) {
  cat("No doctoral alumni listed yet.\n")
} else {
  cat('<div class="student-grid">\n')
  for (s in selected) cat(make_card(s))
  cat('</div>\n')
}
```

## Master alumni {#master-alumni}

```{r}
#| results: asis

selected <- students[vapply(students, function(s) get_value(s, "degree_type") == "Master", logical(1))]

if (length(selected) == 0) {
  cat("No master alumni listed yet.\n")
} else {
  cat('<div class="student-grid">\n')
  for (s in selected) cat(make_card(s))
  cat('</div>\n')
}
```

---

## Alumni by research area {#alumni-by-research-area}

```{r}
#| results: asis

for (topic in all_topics) {
  cat("\n\n### ", esc(topic), " {#", slugify(topic), "}\n\n", sep = "")

  selected <- students[vapply(
    students,
    function(s) topic %in% get_value(s, "topics", list()),
    logical(1)
  )]

  selected <- selected[order(vapply(selected, function(s) -as.numeric(get_value(s, "year", 0)), numeric(1)))]

  for (s in selected) {
    cat("- [", esc(get_value(s, "name")), "](#", esc(get_value(s, "id")), ")", 
        " — ", esc(get_value(s, "thesis")), "\n", sep = "")
  }

  cat("\n[Back to research areas](#research-areas)\n")
}
```
