---
execute:
  echo: false
  warning: false
  message: false
  cache: false
  freeze: false
---

```{r}
library(yaml)
library(htmltools)

courses <- yaml::read_yaml("data/courses.yml")

esc <- function(x) htmltools::htmlEscape(as.character(x))

get_value <- function(x, name, default = "") {
  if (!is.null(x[[name]])) x[[name]] else default
}

slugify <- function(x) {
  x <- tolower(x)
  x <- gsub("[^a-z0-9]+", "-", x)
  x <- gsub("^-|-$", "", x)
  x
}

make_tags <- function(topics) {
  if (length(topics) == 0) return("")
  paste0(
    vapply(
      topics,
      function(topic) {
        paste0('<a class="tag" href="#', slugify(topic), '">', esc(topic), '</a>')
      },
      character(1)
    ),
    collapse = "\n"
  )
}

resource_icon <- function(type) {
  switch(
    type,
    "Syllabus" = "📄",
    "Slides" = "🖥️",
    "Video" = "▶️",
    "Book" = "📘",
    "Lab" = "🧪",
    "Homework" = "✏️",
    "Exam" = "📝",
    "Code/Data" = "💻",
    "Workshop" = "🎤",
    "🔗"
  )
}

make_resources <- function(resources) {
  if (length(resources) == 0) {
    return('<p class="muted">Materials will be added later.</p>')
  }

  items <- vapply(
    resources,
    function(r) {
      type <- get_value(r, "type", "Link")
      paste0(
        '<a class="resource-pill" href="', esc(get_value(r, "url", "#")), '">',
        '<span class="resource-icon">', resource_icon(type), '</span>',
        esc(get_value(r, "text")),
        '</a>'
      )
    },
    character(1)
  )

  paste0('<div class="resource-list">', paste(items, collapse = "\n"), '</div>')
}

make_software <- function(software) {
  if (length(software) == 0) return("")
  paste0(
    '<p class="course-software"><strong>Software:</strong> ',
    esc(paste(software, collapse = ", ")),
    '</p>'
  )
}

make_card <- function(course) {
  paste0(
    '<div class="course-card" id="', esc(get_value(course, "id")), '">\n',
    '<div class="course-card-header">\n',
    '<div>\n',
    '<h3>', esc(get_value(course, "title")), '</h3>\n',
    '<p class="course-meta">', esc(get_value(course, "level")), ' · ', esc(get_value(course, "institution")), '</p>\n',
    '</div>\n',
    '<div class="course-period">', esc(get_value(course, "period")), '</div>\n',
    '</div>\n',
    '<p>', esc(get_value(course, "summary")), '</p>\n',
    make_software(get_value(course, "software", list())), '\n',
    make_tags(get_value(course, "topics", list())), '\n',
    '<h4>Materials</h4>\n',
    make_resources(get_value(course, "resources", list())), '\n',
    '</div>\n'
  )
}

courses <- courses[order(match(vapply(courses, function(x) get_value(x, "level"), character(1)),
                             c("Graduate", "Undergraduate", "Workshop")),
                         vapply(courses, function(x) get_value(x, "title"), character(1)))]

all_topics <- sort(unique(unlist(lapply(courses, function(c) get_value(c, "topics", list())))))

n_courses <- length(courses)
n_graduate <- sum(vapply(courses, function(c) get_value(c, "level") == "Graduate", logical(1)))
n_workshops <- sum(vapply(courses, function(c) get_value(c, "level") == "Workshop", logical(1)))
```

# Teaching

I teach courses in econometrics, spatial econometrics, discrete choice models, microeconomics, and computational methods for applied economic research. Most of my teaching materials emphasize the connection between econometric theory, empirical applications, and implementation in R.

::: {.teaching-summary}
::: {.teaching-stat}
**`r n_courses`**  
Courses and workshops
:::

::: {.teaching-stat}
**`r n_graduate`**  
Graduate courses
:::

::: {.teaching-stat}
**`r n_workshops`**  
Workshops
:::
:::

## Topics {#topics}

```{r}
#| results: asis

for (topic in all_topics) {
  cat('<a class="tag" href="#', slugify(topic), '">', esc(topic), '</a>\n', sep = "")
}
```

---

## Graduate courses {#graduate-courses}

```{r}
#| results: asis

selected <- courses[vapply(courses, function(c) get_value(c, "level") == "Graduate", logical(1))]

cat('<div class="course-grid">\n')
for (course in selected) cat(make_card(course))
cat('</div>\n')
```

## Undergraduate courses {#undergraduate-courses}

```{r}
#| results: asis

selected <- courses[vapply(courses, function(c) get_value(c, "level") == "Undergraduate", logical(1))]

cat('<div class="course-grid">\n')
for (course in selected) cat(make_card(course))
cat('</div>\n')
```

## Workshops {#workshops}

```{r}
#| results: asis

selected <- courses[vapply(courses, function(c) get_value(c, "level") == "Workshop", logical(1))]

cat('<div class="course-grid">\n')
for (course in selected) cat(make_card(course))
cat('</div>\n')
```

---

## Courses by topic {#courses-by-topic}

```{r}
#| results: asis

for (topic in all_topics) {
  cat("\n\n### ", esc(topic), " {#", slugify(topic), "}\n\n", sep = "")

  selected <- courses[vapply(
    courses,
    function(c) topic %in% get_value(c, "topics", list()),
    logical(1)
  )]

  for (course in selected) {
    cat("- [", esc(get_value(course, "title")), "](#", esc(get_value(course, "id")), ")",
        " — ", esc(get_value(course, "summary")), "\n", sep = "")
  }

  cat("\n[Back to topics](#topics)\n")
}
```
